### 2017-04-07 paper/evaluation.tex
minor tweaks in eval.F

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Recall that increased resource contention obtained
with parallelism can lead to concurrency issues such as data races.
Hence, flakiness and speedup are contradictory forces that drive
configuration selection.  Note also that Section~\ref{sec:rqD}
evaluated variable speedup in isolation, focused on project
configuration where parallelism is used by default.

>>>>

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Recall that increased resource contention obtained
with parallelism can lead to concurrency issues such as data races.
Flakiness and speedup are contradictory forces that drive
configuration selection.  Furthermore, note that Section~\ref{sec:rqD}
evaluated speedup in isolation, focused on projects configured to use
parallelism by default.
